Maenpuen et al. Appendix S1-7: Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)

### 2022-04-26 ms/LMA_method.Rmd
update

*Effects of leaf sizes and thicknesses on the relationship between whole-leaf and leaf disc LMA*

@@

where $LMA_{Wi}$, $LMA_{Di}$, $LA_{i}$, $LT_{i}$ are the whole-leaf LMA, leaf disc LMA, leaf area and leaf thickness for tree *i*, respectively.
$\tilde{\mu_i}$ is the effect of leaf area and leaf thickness on the mean estimates for the whole-leaf LMA of tree *i*, and $\sigma_i$ is the variance of whole-leaf LMA for tree *i*, and $\beta$ are coefficients.

>>>>

*Effects of leaf area and thickness on the relationship between whole-leaf and leaf disc LMA*

@@

where $LMA_{Wi}$, $LA_{i}$, $LT_{i}$ are the observed whole-leaf LMA, leaf area and leaf thickness for tree *i*, respectively,
$LMA_{Di}$ is the true unobserved value of leaf disc LMA for tree *i*, which can be modeled using the observed leaf disc LMA.
$\tilde{\mu_i}$ is the effect of leaf area and leaf thickness on the mean estimates for the whole-leaf LMA of tree *i*, and $\sigma_i$ is the variance of whole-leaf LMA for tree *i*, and $\beta$ are coefficients.
